Hyperopt-Sklearn: Subtitle?

### 2014-04-26 papers/2014-automl/paper.tex
paper - add table init
combining pie graphics into one
paper - tbl

\section{Experiments}
We conducted experiments on three data sets to establish that hyperopt-sklearn can find accurate models on a range of data sets
hyperopt-sklearn finds accurate models,
%(b) different data sets lead hyperopt-sklearn to select different models, and
(c) search can be carried out in a reasonable amount of time.
Results were collected on three data sets: MNIST, 20-Newsgroups, and Convex Images.
MNIST~\citep{lecun+bottou+bengio+haffner:1998} is a well-known data set of 70K $28\times 28$ greyscale images of hand-drawn digits.
20-Newsgroups is a 20-way classification data set of 20000 newsgroup messages (we did not remove the headers for our experiments)~\citep{20newsgroups}.
Convex Images~\citep{larochelle+etal:2007} is a binary classification task of distinguishing pictures of convex white-colored regions in small ($32\times 32$) black-and-white images.

To establish that searching the full space is effective,
we performed optimization runs of up to 300 function evaluations searching either the entire space, or else subspaces that corresponded to specific classifier types.
We used three optimization algorithms in Hyperopt: random search, annealing, and TPE.
Figure~\ref{fig:avg_test_scores} shows that the performance of the model found from throughout the entire search space was not statistically inferior to the best model pulled from each classifier subspace;
there was no penalty for keeping all options open during search.
Table~\ref{tbl:opt_scores} lists the test set scores of the best models found by cross-validation, as well as some points of reference from previous work.
Hyperopt-sklearn's scores are relatively good on each data set, indicating that with hyperopt-sklearn's parameterization, Hyperopt's optimization algorithms are competitive with human experts.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{graphics/newsgroups_pie}
    \caption{
	    XXX
    }
    \label{fig:npie}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{graphics/mnist_pie}
    \caption{
	    XXX
    }
    \label{fig:mpie}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{graphics/convex_pie}
    \caption{
	    XXX
    }
    \label{fig:cpie}
\end{figure}

>>>>

\section{Experiments}
We conducted experiments on three data sets to establish that hyperopt-sklearn can find accurate models on a range of data sets
hyperopt-sklearn finds accurate models,
%(b) different data sets lead hyperopt-sklearn to select different models, and
(c) search can be carried out in a reasonable amount of time.
Results were collected on three data sets: MNIST, 20-Newsgroups, and Convex Images.
MNIST~\citep{lecun+bottou+bengio+haffner:1998} is a well-known data set of 70K $28\times 28$ greyscale images of hand-drawn digits.
20-Newsgroups is a 20-way classification data set of 20000 newsgroup messages (\citet{20newsgroups}, we did not remove the headers for our experiments).
Convex Images~\citep{larochelle+etal:2007} is a binary classification task of distinguishing pictures of convex white-colored regions in small ($32\times 32$) black-and-white images.

To establish that searching the full space is effective,
we performed optimization runs of up to 300 function evaluations searching either the entire space, or else subspaces that corresponded to specific classifier types.
We used three optimization algorithms in Hyperopt: random search, annealing, and TPE.
Figure~\ref{fig:avg_test_scores} shows that the performance of the model found from throughout the entire search space was not statistically inferior to the best model pulled from each classifier subspace;
there was no penalty for keeping all options open during search.
Table~\ref{tbl:acc} lists the test set scores of the best models found by cross-validation, as well as some points of reference from previous work.
Hyperopt-sklearn's scores are relatively good on each data set, indicating that with hyperopt-sklearn's parameterization, Hyperopt's optimization algorithms are competitive with human experts.
\citep{eggensperger+etal:2013}
\citep{scipy}.

\begin{table}
    \caption{
        Hyperopt-sklearn scores relative to selections from literature on the three data sets used in our experiments.
        On MNIST, hyperopt-sklearn is one of the best-scoring methods that does not use image-specific domain knowledge (these scores and others may be found at http://yann.lecun.com/exdb/mnist/).
        On 20 Newsgroups, XXX.
        On Convex Images, hyperopt-sklearn outperforms previous automatic algorithm configuration approaches~\citep{eggensperger+etal:2013} and manual tuning~\citep{larochelle+etal:2007}.
    }
    \label{tbl:acc}
    \centering
    \small
    \begin{tabular}{llllll}
        \hline
        \multicolumn{2}{c}{\textbf{MNIST}} & \multicolumn{2}{c}{\textbf{20 Newsgroups}} & \multicolumn{2}{c}{\textbf{Convex Images}}  \\
        Approach & Accuracy  & Approach & Accuracy & Approach & Accuracy\\
        \hline
        Committee of convnets & 99.8\%                & thing & 85\%  & \textbf{hyperopt-sklearn} & 88.9\%\\
        \textbf{hyperopt-sklearn} & \textbf{98.7}\%   & thing & 85\%  & hp-dbnet & 84.6\% \\
        libSVM grid search & 98.6\%                   & thing & 85\% & dbn-3 & 81.4\%\\
        Boosted trees & 98.5\%                        & thing & 85\%  &  &  \\
    \end{tabular}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{graphics/pie}
    \caption{
	    XXX
    }
    \label{fig:npie}
\end{figure}
